### 2018-04-13 results.Rnw
round final DAM results on two steps

Lastly, we can generate a table that compute arbitrary population statistics for each genotype:
<<warning=FALSE>>=
result_dt <- summary_dt[,
          .(
            mean_period = round(mean(first_peak_period, na.rm = T) / hours(1), 2),
            sd_period = round(sd(first_peak_period, na.rm = T) / hours(1), 2),
            percent_rhythmic = round(100 * sum(is_rhythmic) / .N, 2),
            n_rhythmic = sum(is_rhythmic),
            n = .N
            ),
          by = genotype
          ]
result_dt
@

>>>>

Lastly, we can generate a table that compute arbitrary population statistics for each genotype:
<<warning=FALSE>>=
result_dt <- 
  summary_dt[,
    .(
       mean_period = mean(first_peak_period, na.rm = T) / hours(1),
       sd_period = sd(first_peak_period, na.rm = T) / hours(1),
       percent_rhythmic = 100 * sum(is_rhythmic) / .N,
       n_rhythmic = sum(is_rhythmic),
       n = .N
     ),
    by = genotype
  ]

# to round all numeric columns  to two digits
result_dt[, lapply(.SD, function(x) 
				if(is.numeric(x)) round(x, 2) else x
			)]
@
